---
title: "cluster_maker"
author: "Julia Gustavsen"
date: "June 23, 2016"
output: 
    html_document:
      keep_md: true
      number_sections: yes
      theme: cerulean
      toc: yes
      toc_depth: 6 
---

```{r, message = FALSE}
library(RCy3)
library(httr)
library(RJSONIO)
source("./functions_to_add_to_RCy3/working_with_namespaces.R")
```

# Trying out clusterMaker with R 
```{r}
cy <- CytoscapeConnection ()
getCommandsWithinNamespace(cy, "cluster")
```

Following this tutorial: 

http://opentutorials.cgl.ucsf.edu/index.php/Tutorial:Cluster_Maker

# Read in provided session file (.cys file)
```{r}
command.name <- "open"

request.uri <- paste(cy@uri,
                     pluginVersion(cy),
                     "commands/session",
                     as.character(command.name),
                     sep = "/")
## load session
properties.list <- list(file="/home/julia_g/windows_school/gsoc/gsoc_Rcy3_vignettes/data/GalFiltered.cys")
request.res <- GET(url = request.uri,
                   query = properties.list)

getWindowList(cy)

connect_window_to_R_session <- existing.CytoscapeWindow("galFiltered.sif",
                                                        copy.graph.from.cytoscape.to.R = FALSE)
```

Graph from session is loaded into Cytoscape

```{r}
getCommandsWithinNamespace(connect_window_to_R_session, "cluster/hierarchical")
getCommandsWithinNamespace(connect_window_to_R_session, "cluster/getcluster")

```


( from Scooter "cluster getcluster algorithm=hierarchical")

```{r}
node_list <- c("gal1RGexp",
                  "gal4RGexp",
                  "gal80Rexp")

properties.list <- list(
  nodeAttributeList = node_list[1],
                        nodeAttributeList = node_list[2],
                        nodeAttributeList = node_list[3],
                        network = connect_window_to_R_session@title,
                        selectedOnly = FALSE,
                        clusterAttributes = TRUE,
                        ignoreMissing = FALSE,
                        createGroups = TRUE,
                        showUI = FALSE
                        )

command.name <- "hierarchical"
request.uri <- paste(connect_window_to_R_session@uri,
                     pluginVersion(cy),
                     "commands/cluster",
                     as.character(command.name),
                     sep = "/")

request.res <- GET(url = request.uri,
                   query = properties.list,
                   verbose())
request.res$url
http_status(request.res)
```

Need to run a second set of commands to get the clusters
```{r}
command.name <- "getcluster"

properties.list <- list(algorithm = "hierarchical",
                        type = "node")

request.uri <- paste(connect_window_to_R_session@uri,
                     pluginVersion(connect_window_to_R_session),
                     "commands/cluster",
                     as.character(command.name),
                     sep = "/")

request.res <- GET(url = request.uri,
                   query = properties.list,
                   verbose())
request.res$url
http_status(request.res)
request.res$status_code
```


Do I get http://localhost:1234/v1/commands/cluster/getcluster?algorithm=hierarchical&type=node

This puts the clusters into the network table in Cytoscape.

How to work with this? Need to look at network table. 
```{r, cache=TRUE}
request.uri <- paste(connect_window_to_R_session@uri,
                     pluginVersion(connect_window_to_R_session),
                     "networks",
                     connect_window_to_R_session@window.id,
                     "tables/defaultnetwork",
                     sep = "/")

## can view at http://localhost:1234/v1/networks/15728/tables/defaultnetwork under node_clusters
request.res <- GET(request.uri) # returns all of the node SUIDs

cluster_content <- fromJSON(rawToChar(request.res$content))
  
## returns the clusters to which each node belongs.           
cluster_content$rows[[1]]$`__nodeClusters`
```

Not currently working. Should have a list of all of the clusters and the membership of each node. 
