---
title: "data_sets_in_RCy3"
author: "Julia Gustavsen"
date: "May 24, 2016"
output: html_document
---

Can I just use some of the virus data?

TARA ocean data: http://www.raeslab.org/companion/ocean_interactome/taxonMatrices.zip

What about a small subset of the human gut data? what about the Faust lab?

http://onlinelibrary.wiley.com/doi/10.15252/msb.20156272/pdf

library(igraph)
library(igraphdata)
data(package="igraphdata")
data(foodwebs)
plot(foodwebs$mangwet)
data(yeast)

Ok finally the idea is that I can have one with made up data and then I can use the Tara Oceans data to look at another vignette. 

Let's just make it up so it doesn't depend on anything for now...

```{r}
library(RCy3)
library(igraph)
library(RJSONIO)
species_data <- read.table(header=T, row.names=1, text=
"    Species1 Species2 Species3 Species4
 1   1   1   0  2
 2   1   0   1  3
 3   1   2   1  4
 4   0   3   1  2
 5   2   0   0  0
 6   2   1   1  1
")

spe_cor <- cor(as.matrix(species_data),
                  method="spearman") 

spe_cor[upper.tri(spe_cor)] <- NA
library(reshape2)
melted_cor <- melt(spe_cor)
melted_cor <- na.omit(melted_cor)

library(dplyr)
filtered_data <- filter(melted_cor, abs(value) > 0.6)

graph_spe <- graph.data.frame(filtered_data,
                          directed=FALSE)

plot(graph_spe)
```
 
Williams et al did a good job here:

http://co-occurrence.readthedocs.io/en/latest/

 
Previously used
```{r}
library(vegan)
data(dune)
dune
```

Let's try to send the first one to Cytoscape

Oh RCy3 doesn't work with igraph!

Can that be fixed? Or should it be?

Can I try to use graph instead?


```{r}
## ok can quickly do this:

graphNEL_spe <- igraph.to.graphNEL(graph_spe)
plot(graphNEL_spe)
graphNEL_spe <- initEdgeAttribute (graphNEL_spe, "weight", "integer", 3)
graphNEL_spe <- initEdgeAttribute (graphNEL_spe, "value", "numeric", 1.0)
## so this just changes these things to these values.
## doesn't use the underlying data. A bit hard to work with.

# plot(graphNEL_spe)
# g <- new ('graphNEL', edgemode='directed')
# g <- graph::addNode ('A', g)
# g <- graph::addNode ('B', g)
# g <- graph::addNode ('C', g)

## can figure out later how to do with graph package
## g <- new ('graphNEL', edgemode='directed')
cw <- CytoscapeWindow('co-occurrence',
                      graph=graphNEL_spe,
                      overwrite=TRUE)
displayGraph(cw)
```


next in their vignette

the layout

```{r}
layoutNetwork (cw, layout.name='grid')
```

# Add node attributes

```{r}
    g <- cw@graph   # created above, in the section  'A minimal example'
    g <- initNodeAttribute (graph=g,
                            attribute.name='Family',
                            attribute.type='char',
                            default.value='undefined')
    nodeData (g, 'Species1', 'Family') <- 'Family1'
    nodeData (g, 'Species2', 'Family') <- 'Family2'
    nodeData (g, 'Species3', 'Family') <- 'Family1'
    nodeData (g, 'Species4', 'Family') <- 'Family1'
g <- initNodeAttribute (graph=g,  'lfc', 'numeric', 0.0)
    nodeData (g, 'Species1', 'lfc') <- -1.2
    nodeData (g, 'Species2', 'lfc') <- 1.8
    nodeData (g, 'Species3', 'lfc') <- 3.2
    nodeData (g, 'Species4', 'lfc') <- 0.0    
## setGraph?? maybe the documentation is a bit hard to understand if you do not know S4?
    ## so other things can be assigned in the other slots?
    cw <- setGraph(cw, g)
    str(cw)
    displayGraph(cw)    # cw's graph is sent to Cytoscape

```

Ok now see these attributes show up in Cytoscape

# Set up the default colours in cytoscape
```{r}
    setDefaultNodeShape(cw, 'OCTAGON')
    setDefaultNodeColor(cw, '#AAFF88')
    setDefaultNodeSize(cw, 80)
    setDefaultNodeFontSize(cw, 40)
```


## Map attributes

So first we look at ways of getting the info from cytoscape so that we can work with it. Interactive a bit. 

```{r}
getNodeShapes(cw)   # diamond, ellipse, trapezoid, triangle, etc.
## noa.names --make title more informatic Names of node attributes
print(noa.names(getGraph(cw)))  # what data attributes are defined?
print(noa(getGraph(cw),
          'moleculeType'))
print(noa(getGraph(cw),
          'Family'))   

attribute.values <- c('Family1',
                      'Family2')
node.shapes      <- c('DIAMOND',
                      'TRIANGLE')
    
## this applies the rule
setNodeShapeRule(cw,
                 node.attribute.name='Family',
                 attribute.values,
                 node.shapes)
```


## Interpolation rules

used for values that can vary of are between certain levels
```{r}
setNodeColorRule(cw,
                 'lfc',
                 c(-3.0,
                   0.0,
                   3.0),
                 c('#00AA00',
                   '#00FF00',
                   '#FFFFFF',
                   '#FF0000',
                   '#AA0000'),
                 mode='interpolate')
```

Note that there \emph{five} colors, but only three control.points. The two additional colors tell the interpolated mapper which colors to use if the stated data attribute (lfc) has a value less than the smallest control point (paint it a darkish green, \#00AA00) or larger than the largets control point (paint it a darkish red, \#AA0000).  These extreme (or out-of-bounds) colors may be omitted:


## Interpolating node size

```{r}
control.points = c (-1.2,
                    2.0,
                    4.0)
node.sizes     = c (10,
                    20,
                    50,
                    200,
                    205)
setNodeSizeRule (cw,
                 'lfc',
                 control.points,
                 node.sizes,
                 mode='interpolate')
```

# Edge attributes

```{r}
g <- cw@graph
g <- initEdgeAttribute(graph=g,
                       attribute.name='edgeType',
                       attribute.type='char',
                       default.value='unspecified')
edgeData(g, 'Species1', 'Species2', 'edgeType') <- 'phosphorylates'
edgeData(g, 'Species1', 'Species4', 'edgeType') <- 'promotes'
## so this added edges

    
cw@graph <- g
displayGraph (cw)
    
line.styles = c ('DOT', 'SOLID')
edgeType.values = c ('phosphorylates', 'promotes')
setEdgeLineStyleRule (cw,
                      'edgeType',
                      edgeType.values,
                      line.styles)
    
arrow.styles = c('Arrow', 'Delta')
setEdgeTargetArrowRule(cw,
                       'edgeType',
                       edgeType.values,
                       arrow.styles)
```

# Manipulating the cytoscape window

could be very useful for the use with a monitor

```{r}
hidePanel (cw, 'Data Panel')
floatPanel (cw, 'D')
dockPanel (cw, 'd')
hidePanel (cw, 'Control Panel')
floatPanel (cw, 'control')
dockPanel (cw, 'c')
```


Selecting specific nodes
```{r}
selectNodes(cw, 'Family1') # gives error
selectNodes(cw, 'Species1')
```


Here could get a list of those selected

```{r}
getSelectedNodes(cw)
selectFirstNeighborsOfSelectedNodes(cw)
selected_nodes <- getSelectedNodes(cw)
```



layout  that is data driven.
what is makeSimpleGraph()?? 3 nodes good for demos...

```{r}
help("makeSimpleGraph")
cwe <- CytoscapeWindow('vignette.setNodePosition',
                            graph=RCy3::makeSimpleGraph(),
                       overwrite=TRUE)
displayGraph(cwe)
    layoutNetwork(cwe,
                  'grid')
    
center.x <- 200
center.y <- 200
radius <- 200

# sweep through full revolution 3 times, 5 degrees at a time
angles <- seq (0, 360, 90)
for (angle in angles) {
  angle.in.radians <- angle * pi / 180
  x <- center.x + (radius * cos (angle.in.radians))
  y <- center.y + (radius * sin (angle.in.radians))
  setNodePosition (cwe, 'A', x, y)
}

```

What about printing window to a pdf or png??

```{r}
saveImage(cw,"test", "pdf", scale=1.0)
saveImage(cw,"test", "png", scale=0.3)
## shouldn't saveImage have in the See Also section something about saving session?
saveNetwork(cw, "test") ## makes test.cys, which is not a session file and I am not sure what to do with it...
## what about a saveSession idea??
```


# Send network to Cytoscape

```{r}
## can I somehow port this function to RCy3?
toCytoscape <- function (igraphobj) {
  # Extract graph attributes
  graph_attr = graph.attributes(igraphobj)
  # Extract nodes
  node_count = length(V(igraphobj))
  if('name' %in% list.vertex.attributes(igraphobj)) {
    V(igraphobj)$id <- V(igraphobj)$name
  } else {
    V(igraphobj)$id <- as.character(c(1:node_count))
  }
  
  nodes <- V(igraphobj)
  v_attr = vertex.attributes(igraphobj)
  v_names = list.vertex.attributes(igraphobj)
  
  nds <- array(0, dim=c(node_count))
  for(i in 1:node_count) {
    if(i %% 1000 == 0) {
      print(i)
    }
    nds[[i]] = list(data = mapAttributes(v_names, v_attr, i))
  }
  
  edges <- get.edgelist(igraphobj)
  edge_count = ecount(igraphobj)
  e_attr <- edge.attributes(igraphobj)
  e_names = list.edge.attributes(igraphobj)
  
  attr_exists = FALSE
  e_names_len = 0
  if(identical(e_names, character(0)) == FALSE) {
    attr_exists = TRUE
    e_names_len = length(e_names)
  }
  e_names_len <- length(e_names)
  
  eds <- array(0, dim=c(edge_count))
  for(i in 1:edge_count) {
    st = list(source=toString(edges[i,1]), target=toString(edges[i,2]))
    
    # Extract attributes
    if(attr_exists) {
      eds[[i]] = list(data=c(st, mapAttributes(e_names, e_attr, i)))
    } else {
      eds[[i]] = list(data=st)
    }

    if(i %% 1000 == 0) {
      print(i)
    }
  }
  
  el = list(nodes=nds, edges=eds)
  
  x <- list(data = graph_attr, elements = el)
  print("Done.  To json Start...")
  return (toJSON(x))
}

mapAttributes <- function(attr.names, all.attr, i) {
  attr = list()
  cur.attr.names = attr.names
  attr.names.length = length(attr.names)
  
  for(j in 1:attr.names.length) {
    if(is.na(all.attr[[j]][i]) == FALSE) {
      #       attr[j] = all.attr[[j]][i]
      attr <- c(attr, all.attr[[j]][i])
    } else {
      cur.attr.names <- cur.attr.names[cur.attr.names != attr.names[j]]
    }
  }
  names(attr) = cur.attr.names
  return (attr)
}





```



```{r}
cy <- CytoscapeConnection ()
deleteAllWindows(cy)
phage_and_prok_dcm <- read.delim("./data/taxonMatrices/matrix_23.txt")

## did work on them in "inst/data-raw/"

## but don't know if virus or prok....could fix that.
## this is too big!!!
#library(httr)
prok_vir_cor <- read.delim("./data/virus_prok_cor.tsv")

graph_vir_prok <- simplify(graph.data.frame(prok_vir_cor,
                               directed=FALSE))

# #plot(graph_dune)
# port.number = 1234
# 
# base.url = paste("http://localhost:",
#                  toString(port.number),
#                  "/v1", sep="")
# base.url
# 
# cygraph <- toCytoscape(graph_vir_prok) ## formats an igraph object to json for sending to Cytoscape
# 
# network.url <-  paste(base.url,
#                       "networks",
#                       sep="/")
# 
# res <- POST(url=network.url,
#             body=cygraph,
#             encode="json")

```

need to find a way to send igraphs to cytoscape via Rcy3 too. 

```{r}
#something like CytoscapeWindow...

# Check the attributes
summary(graph_vir_prok)
gD.cyt <- igraph.to.graphNEL(graph_vir_prok)
# g <- gD.cyt@
#     g <- cw@graph 
#     g <- initNodeAttribute (graph=g,  attribute.name='moleculeType',
#                             attribute.type='char',
#                             default.value='undefined')
summary(gD.cyt)
nodeData(gD.cyt)
edgeData(gD.cyt)
edgeNames(gD.cyt)
properlyInitializedNodeAttribute(gD.cyt, "name")
eda.names(gD.cyt) ## properly initialized

## where does is.classic.graph(graph) come from??
getEdgeAttributeNames(gD.cyt)
gD.cyt <- initEdgeAttribute (graph=gD.cyt,
                             "weight",
                             'numeric',
                             0.0)

gDCW <- CytoscapeWindow("Les Miserables",
                        graph = gD.cyt,
                        overwriteWindow = TRUE)
getEdgeAttributeNames(gDCW)
cw <- setGraph (gDCW, gD.cyt)
displayGraph (cw)

# We can display graph, with defaults color/size scheme
displayGraph(gDCW)


gD.cyt <- igraph.to.graphNEL(gD)
igraph.from.graphNEL(gD, name = TRUE, weight = TRUE, unlist.attrs = TRUE)
# We have to create attributes for graphNEL
# We'll keep the same name, so the values are passed from igraph

gD.cyt <- initNodeAttribute(gD.cyt, 'degree', 'numeric', 0) 
gD.cyt <- initNodeAttribute(gD.cyt, 'betweenness', 'numeric', 0) 
gD.cyt <- initEdgeAttribute (gD.cyt, "weight", 'integer', 0)
gD.cyt <- initEdgeAttribute (gD.cyt, "similarity", 'numeric', 0)

# Now we can create a new graph window in cytoscape
# Be sure that CytoscapeRPC plugin is activated
gDCW <- CytoscapeWindow("Les Miserables",
                        graph = gD.cyt,
                        overwriteWindow = TRUE)

# We can display graph, with defaults color/size scheme
displayGraph(gDCW)

# If you also want to choose a layout from R, a list  of available layouts can be accessed as follows:
cy <- CytoscapeConnection()
hlp <-getLayoutNames(cy)
# We'll select the layour number 18 - "fruchterman-rheingold" layout 
# See properties for the given layout
# getLayoutPropertyNames(cy, hlp[18])
# Apply values to some of the properties and plot the layout
setLayoutProperties (gDCW,
                     hlp[18],
                     list (edge_attribute = 'similarity', iterations = 1000))
layoutNetwork(gDCW, hlp[18])

# Figure 1 made here

# Now, we can define our own default color/size scheme
setDefaultBackgroundColor(gDCW, '#FFFFFF')
setDefaultEdgeColor(gDCW, '#CDC9C9')
setDefaultEdgeLineWidth(gDCW, 4)
setDefaultNodeBorderColor(gDCW, '#000000')
setDefaultNodeBorderWidth(gDCW, 3)
setDefaultNodeShape(gDCW, 'ellipse')
setDefaultNodeColor(gDCW, '#87CEFA')
setDefaultNodeSize(gDCW, 60)
setDefaultNodeFontSize(gDCW, 20)
setDefaultNodeLabelColor(gDCW, '#000000')

# And we can replot it 
redraw(gDCW)    
```




```{r}
ug <- ftM2graphNEL(as.matrix(prok_vir_cor[1:2]),
                   edgemode = "directed",
                   W = as.matrix(prok_vir_cor[3]))
edgeWeights(ug)

#ug <- ftM2graphNEL(as.matrix(prok_vir_cor[1:2]))

# ug <- initEdgeAttribute (ug, "weight", "numeric",prok_vir_cor[3] )

#ug <- initEdgeAttribute (ug, "weight", "numeric",0 )

cw <- CytoscapeWindow('co-occurrence',
                      graph=ug,
                      overwrite=TRUE)

displayGraph(cw)
```



```{r}

# ## need to get it to work with igrpah....this graph bioconductor sucks...
# port.number=1234
# 
# base.url = paste("http://localhost:", toString(port.number), "/v1", sep="")
# cygraph <- toCytoscape(graph_vir_prok) 
# library(httr)
# network.url = paste(base.url, "networks", sep="/")
# res <- POST(url=network.url, body=cygraph, encode="json")

```

