---
title: "playing_around_with_RCy3_functions"
author: "Julia Gustavsen"
date: "May 24, 2016"
output: 
    html_document:
      keep_md: true
      number_sections: yes
      theme: cerulean
      toc: yes
      toc_depth: 6        
---

# Purpose

Testing out some ways to develop functions that could be used in R with RCy3 to access Cytoscape plugins

# Sandbox

```{r}
library(RCy3)
library(RJSONIO)
library(httr)
```

## Connection to Cytoscape 

```{r}
CytoscapeConnection() # checks for the connection
CytoscapeWindow("test", overwriteWindow = TRUE) # creates empty window in Cytoscape
existing.CytoscapeWindow("new") # throws an error if it does not exist yet
existing.CytoscapeWindow("test") # The constructor for the CytoscapeWindowClass, used when Cytoscape already contains 
## and displays a network. COuld be useful. 

#check.cytoscape.plugin.version() ## doesn't work with loading the regular library. or in dev. Seems to work a bit more if loaded separately

```

## Visualizing REST urls

```{r}
port.number = 1234
base.url = paste("http://localhost:",
                 toString(port.number),
                 "/v1", sep="")
base.url


```

## Basic cytoscape info

```{r}
version.url = paste(base.url,
                    "version",
                    sep="/")

cytoscape.version = GET(version.url)
cy.version = fromJSON(rawToChar(cytoscape.version$content))
cy.version

basic_info = GET(base.url)

basic_info = fromJSON(rawToChar(basic_info$content))
basic_info
```


## List of networks currently available

```{r}
## lists networks 
network.url = paste(base.url, "networks", sep="/")
network.url
```

## Code from RCy3 on getLayoutNames

Help to figure out how to access the commands for manipulating networks n Cytoscape via plugins. 

standardGeneric() is like the S3 UseMethod()
```{r}
## lifted from RCy3 code

setMethod('getLayoutNames',
          'CytoscapeConnectionClass', 
          function(obj) {
            request.uri <- paste(obj@uri,
                                 pluginVersion(obj),
                                 "apply/layouts",
                                 sep="/")
            request.res <- GET(url=request.uri)
            
            available.layouts <- unname(fromJSON(rawToChar(request.res$content)))
            return(available.layouts)
          })
```

To look at the current parameters of one type of attribute: 

http://localhost:1234/v1/apply/layouts/attribute-circle/parameters

Will come back later to find the function that RCy3 uses to apply parameters

```{r}
cy <- CytoscapeConnection ()
getLayoutNames (cy)
```

## URLs used to test out API calls

http://localhost:1234/v1/networks - gives list of networks

http://localhost:1234/v1/networks/13633 - gives json formatted view of network

http://localhost:1234/v1/networks/13633/tables - shows all networks?

http://localhost:1234/v1/networks/13633/tables/defaultnode

http://localhost:1234/v1/networks/13633/tables/defaultnode/rows

http://localhost:1234/v1/networks/13633/tables/defaultedge

http://localhost:1234/v1/networks/13633/tables/defaultedge/rows

http://localhost:1234/v1/apply/styles

http://localhost:1234/v1/networks.names/ - returns json list

http://localhost:1234/v1/tables/count/


