---
title: "playing_with_RCy3_vignette"
author: "Julia Gustavsen"
date: "June 28, 2016"
output: 
    html_document:
      keep_md: true
      number_sections: yes
      theme: cerulean
      toc: yes
      toc_depth: 6 
---

```{r, message=FALSE}
library(RCy3)
library(igraph)
library(RJSONIO)
library(reshape2)
library(dplyr)

species_data <- read.table(header=T, row.names=1, text=
"    Species1 Species2 Species3 Species4
 1   1   1   0  2
 2   1   0   1  3
 3   1   2   1  4
 4   0   3   1  2
 5   2   0   0  0
 6   2   1   1  1
")

spe_cor <- cor(as.matrix(species_data),
                  method="spearman") 

spe_cor[upper.tri(spe_cor)] <- NA

melted_cor <- melt(spe_cor)
melted_cor <- na.omit(melted_cor)


filtered_data <- filter(melted_cor, abs(value) > 0.6)

graph_spe <- graph.data.frame(filtered_data,
                          directed=FALSE)

plot(graph_spe)
```
 
Williams et al did a good job here:

http://co-occurrence.readthedocs.io/en/latest/

 
Let's try to send the first one to Cytoscape

Oh RCy3 doesn't work with igraph!

Can that be fixed? Or should it be?

Can I try to use graph instead?


```{r}
## ok can quickly do this:
graphNEL_spe <- igraph.to.graphNEL(graph_spe)
plot(graphNEL_spe)
graphNEL_spe <- initEdgeAttribute (graphNEL_spe,
                                   "weight",
                                   "integer",
                                   3)
graphNEL_spe <- initEdgeAttribute (graphNEL_spe,
                                   "value", 
                                   "numeric",
                                   1.0)

cw <- CytoscapeWindow('co-occurrence',
                      graph=graphNEL_spe,
                      overwrite=TRUE)
displayGraph(cw)
```


next in their vignette

the layout

```{r}
layoutNetwork(cw, layout.name='grid')
```

# Add node attributes

```{r}
g <- cw@graph   # created above, in the section  'A minimal example'
g <- initNodeAttribute (graph=g,
                            attribute.name='Family',
                            attribute.type='char',
                            default.value='undefined')
nodeData(g, 'Species1', 'Family') <- 'Family1'
nodeData(g, 'Species2', 'Family') <- 'Family2'
nodeData(g, 'Species3', 'Family') <- 'Family1'
nodeData(g, 'Species4', 'Family') <- 'Family1'
    
g <- initNodeAttribute (graph=g,  'lfc', 'numeric', 0.0)
nodeData(g, 'Species1', 'lfc') <- -1.2
nodeData(g, 'Species2', 'lfc') <- 1.8
nodeData(g, 'Species3', 'lfc') <- 3.2
 nodeData(g, 'Species4', 'lfc') <- 0.0    
## setGraph?? maybe the documentation is a bit hard to understand if you do not know S4?
    ## so other things can be assigned in the other slots?
cw <- setGraph(cw, g)
str(cw)
displayGraph(cw)    # cw's graph is sent to Cytoscape

```

Ok now see these attributes show up in Cytoscape

# Set up the default colours in cytoscape
```{r}
setDefaultNodeShape(cw, 'OCTAGON')
setDefaultNodeColor(cw, '#AAFF88')
setDefaultNodeSize(cw, 80)
 setDefaultNodeFontSize(cw, 40)
```


## Map attributes

So first we look at ways of getting the info from cytoscape so that we can work with it. Interactive a bit. 

```{r}
getNodeShapes(cw)   # diamond, ellipse, trapezoid, triangle, etc.
## noa.names --make title more informatic Names of node attributes
print(noa.names(getGraph(cw)))  # what data attributes are defined?
print(noa(getGraph(cw),
          'moleculeType'))
print(noa(getGraph(cw),
          'Family'))   

attribute.values <- c('Family1',
                      'Family2')
node.shapes      <- c('DIAMOND',
                      'TRIANGLE')
    
## this applies the rule
setNodeShapeRule(cw,
                 node.attribute.name='Family',
                 attribute.values,
                 node.shapes)
```


## Interpolation rules

used for values that can vary of are between certain levels
```{r}
setNodeColorRule(cw,
                 'lfc',
                 c(-3.0,
                   0.0,
                   3.0),
                 c('#00AA00',
                   '#00FF00',
                   '#FFFFFF',
                   '#FF0000',
                   '#AA0000'),
                 mode='interpolate')
```

Note that there \emph{five} colors, but only three control.points. The two additional colors tell the interpolated mapper which colors to use if the stated data attribute (lfc) has a value less than the smallest control point (paint it a darkish green, \#00AA00) or larger than the largets control point (paint it a darkish red, \#AA0000).  These extreme (or out-of-bounds) colors may be omitted:


## Interpolating node size

```{r}
control.points = c (-1.2,
                    2.0,
                    4.0)
node.sizes     = c (10,
                    20,
                    50,
                    200,
                    205)
setNodeSizeRule (cw,
                 'lfc',
                 control.points,
                 node.sizes,
                 mode='interpolate')
```

# Edge attributes

```{r}
g <- cw@graph
g <- initEdgeAttribute(graph=g,
                       attribute.name='edgeType',
                       attribute.type='char',
                       default.value='unspecified')
edgeData(g, 'Species1', 'Species2', 'edgeType') <- 'phosphorylates'
edgeData(g, 'Species1', 'Species4', 'edgeType') <- 'promotes'
## so this added edges

    
cw@graph <- g
displayGraph (cw)
    
line.styles = c ('DOT', 'SOLID')
edgeType.values = c ('phosphorylates', 'promotes')
setEdgeLineStyleRule (cw,
                      'edgeType',
                      edgeType.values,
                      line.styles)
    
arrow.styles = c('Arrow', 'Delta')
setEdgeTargetArrowRule(cw,
                       'edgeType',
                       edgeType.values,
                       arrow.styles)
```

# Manipulating the cytoscape window

could be very useful for the use with a monitor

```{r}
hidePanel(cw, 'Data Panel')
floatPanel(cw, 'D')
dockPanel(cw, 'd')
hidePanel(cw, 'Control Panel')
floatPanel(cw, 'control')
dockPanel(cw, 'c')
```


Selecting specific nodes
```{r}
selectNodes(cw, 'Family1') # gives error
selectNodes(cw, 'Species1')
```


Here could get a list of those selected

```{r}
getSelectedNodes(cw)
selectFirstNeighborsOfSelectedNodes(cw)
selected_nodes <- getSelectedNodes(cw)
```

What about printing window to a pdf or png??

```{r}
saveImage(cw,"test", "pdf", scale=1.0)
saveImage(cw,"test", "png", scale=0.3)
## shouldn't saveImage have in the See Also section something about saving session?
saveNetwork(cw, "test") ## makes test.cys, which is not a session file and I am not sure what to do with it...
## what about a saveSession idea??
```


# Send network to Cytoscape

Function to be ported to RCy3??
```{r}
## can I somehow port this function to RCy3?
toCytoscape <- function (igraphobj) {
  # Extract graph attributes
  graph_attr = graph.attributes(igraphobj)
  # Extract nodes
  node_count = length(V(igraphobj))
  if('name' %in% list.vertex.attributes(igraphobj)) {
    V(igraphobj)$id <- V(igraphobj)$name
  } else {
    V(igraphobj)$id <- as.character(c(1:node_count))
  }
  
  nodes <- V(igraphobj)
  v_attr = vertex.attributes(igraphobj)
  v_names = list.vertex.attributes(igraphobj)
  
  nds <- array(0, dim=c(node_count))
  for(i in 1:node_count) {
    if(i %% 1000 == 0) {
      print(i)
    }
    nds[[i]] = list(data = mapAttributes(v_names, v_attr, i))
  }
  
  edges <- get.edgelist(igraphobj)
  edge_count = ecount(igraphobj)
  e_attr <- edge.attributes(igraphobj)
  e_names = list.edge.attributes(igraphobj)
  
  attr_exists = FALSE
  e_names_len = 0
  if(identical(e_names, character(0)) == FALSE) {
    attr_exists = TRUE
    e_names_len = length(e_names)
  }
  e_names_len <- length(e_names)
  
  eds <- array(0, dim=c(edge_count))
  for(i in 1:edge_count) {
    st = list(source=toString(edges[i,1]), target=toString(edges[i,2]))
    
    # Extract attributes
    if(attr_exists) {
      eds[[i]] = list(data=c(st, mapAttributes(e_names, e_attr, i)))
    } else {
      eds[[i]] = list(data=st)
    }

    if(i %% 1000 == 0) {
      print(i)
    }
  }
  
  el = list(nodes=nds, edges=eds)
  
  x <- list(data = graph_attr, elements = el)
  print("Done.  To json Start...")
  return (toJSON(x))
}

mapAttributes <- function(attr.names, all.attr, i) {
  attr = list()
  cur.attr.names = attr.names
  attr.names.length = length(attr.names)
  
  for(j in 1:attr.names.length) {
    if(is.na(all.attr[[j]][i]) == FALSE) {
      #       attr[j] = all.attr[[j]][i]
      attr <- c(attr, all.attr[[j]][i])
    } else {
      cur.attr.names <- cur.attr.names[cur.attr.names != attr.names[j]]
    }
  }
  names(attr) = cur.attr.names
  return (attr)
}

```

